An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-21 VLDB2026/main.tex
1

	WinFilter and ACORN-\(\gamma\) take the longest.
	WinFilter relies on a tree structure, requiring separate nearest-neighbor graphs per node. This causes redundant computation and high costs, especially for large datasets.
	ACORN-\(\gamma\) expands the neighbor list of each node to provide more candidate paths, which increases both computation and storage costs. It also prunes distant neighbors to save storage space. However, this introduces additional overhead and slows down the construction process.

>>>>

	WinFilter and ACORN-\(\gamma\) take the longest.
	WinFilter relies on a tree structure, requiring separate nearest-neighbor graphs per node. This causes redundant computation and high costs, especially for large datasets.
	ACORN-\(\gamma\) expands the neighbor list of each node to provide more candidate paths, which increases both computation and storage costs. It also prunes distant neighbors to save storage space. However, this introduces additional overhead and slows down the construction process.\textcolor{orange}{In contrast, as we have analyzed in the corresponding section on attribute filtering, ACORN-1 trades efficiency for accuracy, so the construction time is short. SeRF is built on HNSW, so the time is similar to and slightly lower than ACORN-1.}
